Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-21 paper_comparison/appendix.Rmd
replace numbers with letters

---
title: "Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference"
output: pdf_document
author: "Weihao Li, Dianne Cook, Emi Tanaka and Susan VanderPlas"
bibliography: "paper_comparison/paper.bib"
---

@@

>>>>

---
title: "Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference"
output: 
  pdf_document:
    number_sections: true
author: "Weihao Li, Dianne Cook, Emi Tanaka and Susan VanderPlas"
bibliography: "paper_comparison/paper.bib"
header-includes:
  - \renewcommand\thesection{\Alph{section}}
  - \renewcommand\thesubsection{\thesection.\arabic{subsection}}
---

@@

## Effect of number of evaluations on the power of a visual test

## Power of a RESET test under different auxiliary regression formulas
